Global optimization method with dual Lipschitz constant estimates for problems with non-convex constraints

### 2020-01-21 2019/NUMTA_Barkalov/Special Issure/article.tex
add acknowledgments

	The dimensionality reduction scheme considered here matches a multidimensional problem with Lipschitzian minimized function and Lipschitzian constraints to a one-dimensional problem, in which the corresponding functions satisfy the uniform H\"{o}lder condition (see \cite{Strongin2000, Sergeyev2013}), i.e.
$$
	\left|g_j(y(x'))-g_j(y(x''))\right| \leq K_j \left|x'-x'' \right|^{1/N}, \; x', x''\in [0,1], \; 1\leq j \leq m+1,
$$
where $N$ is the dimensionality of the initial multidimensional problem and the coefficients $K_j$ are related to the Lipschitz constants $L_j$ of the initial problem by the relations
\begin{equation}\label{K_leq_L}
	K_j \leq 2L_j \sqrt{N+3}, \; 1\leq j \leq m+1.
\end{equation}

@@

>>>>

	The dimensionality reduction scheme considered here matches a multidimensional problem with Lipschitzian objective function and Lipschitzian constraints to a one-dimensional problem, in which the corresponding functions satisfy the uniform H\"{o}lder condition (see \cite{Strongin2000, Sergeyev2013}), i.e.
$$
	\left|g_j(y(x'))-g_j(y(x''))\right| \leq K_j \left|x'-x'' \right|^{1/N}, \; x', x''\in [0,1], \; 1\leq j \leq m+1,
$$
where $N$ is the dimensionality of the initial multidimensional problem and the coefficients $K_j$ are related to the Lipschitz constants $L_j$ of the initial problem by the relations
\begin{equation}\label{K_leq_L}
	K_j \leq 2L_j \sqrt{N+3}, \; 1\leq j \leq m+1.
\end{equation}

@@

\section*{Acknowledgments}
This research was supported by the Russian Science Foundation, project No. 16-11-10150.
